---
title: "P8105 Homework 1 fb2731"
author: "fan bu"
output: github_document
date: "2026-09-26"
---

```{r setup, message=FALSE, warning=FALSE}
library(tidyverse)
```
# Problem 1

```{r load-penguins}
data("penguins", package = "palmerpenguins")
```
The `penguins` dataset contains information on three penguin species:
`r paste(levels(penguins$species), collapse = ", ")`.
Important variables include species, island, bill length, bill depth,
flipper length, body mass, sex, and year.

The dataset contains `r nrow(penguins)` observations and
`r ncol(penguins)` variables.

The mean flipper length is
`r round(mean(penguins$flipper_length_mm, na.rm = TRUE), 2)` mm.
## Scatterplot

The following scatterplot shows flipper length versus bill length, with
points colored according to penguin species.

```{r penguin-plot}
penguin_plot =
  ggplot(
    penguins,
    aes(
      x = bill_length_mm,
      y = flipper_length_mm,
      color = species
    )
  ) +
  geom_point() +
  labs(
    x = "Bill Length (mm)",
    y = "Flipper Length (mm)",
    color = "Species",
    title = "Flipper Length vs Bill Length"
  )

penguin_plot
```
```{r save-plot}
ggsave(
  filename = "penguin_scatterplot.png",
  plot = penguin_plot
)
```
# Problem 2
```{r create-dataframe}
set.seed(123)

hw_df =
  tibble(
    normal_sample = rnorm(10),
    positive = normal_sample > 0,
    character_var = c(
      "a", "b", "c", "d", "e",
      "f", "g", "h", "i", "j"
    ),
    factor_var = factor(
      c(
        "low", "medium", "high", "low", "medium",
        "high", "low", "medium", "high", "low"
      )
    )
  )

hw_df
```
## Means of the variables

```{r variable-means}
mean(pull(hw_df, normal_sample))

mean(pull(hw_df, positive))

mean(pull(hw_df, character_var))

mean(pull(hw_df, factor_var))
```
## Type coercion

```{r coercion, results='hide'}
as.numeric(pull(hw_df, positive))

as.numeric(pull(hw_df, character_var))

as.numeric(pull(hw_df, factor_var))
```
results='hide'